### 2021-11-07 New-Manuscript/sections/adp_model.tex
completed simulation

\begin{fleqn}[\parindent]
	\begin{equation}\begin{alignedat}{10}
			& \beta^{pw}_{mdkc}: \qquad 
				&& 	\sum_{dkc} \beta_{0dkc}^{pw} \Big( pw_{0dkc} - \gamma (pea_{dkc}) \Big) +
					\sum_{m=1dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
					\Big( pw_{mdkc} - \gamma 
					(\hat{pw}_{m-1dkc}) \Big) + \\
			& 
				&& \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
					\Big( pw_{mdkc} - \gamma 
					(\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - + E[pwt\_k_{k}]) \Big) + \\
			& 
				&& \sum_{dc} \beta_{Mdkc}^{pw} 
					\Big( pw_{Mdkc} - \gamma \sum_{M-1}^{M}
					(\hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big)
	\end{alignedat} \end{equation}
\end{fleqn}

@@

\begin{equation}\begin{alignedat}{10}
		&	v(S') = \Bigg( 
		&& 	\beta^0 + 
		\bigg( \sum_{p} \beta_{1p}^{ue} 
		(uen_{d} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
		\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\
		&	&& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
		( \hat{uu}_{t+1,p} + \sum_{mdc} E[pst_{tmdc}] (U_{pd+1c} - U_{pdc})) \bigg) + \\
		&	&&	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
		(\sum_{M-1}^{M} \hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}])\bigg) + \\
		& 	&&	\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \bigg) + \\	
		&	&&	\qquad \qquad \bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
		(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}])) \bigg)
		\Bigg)
	\end{alignedat}
\end{equation}

>>>>

\begin{fleqn}[\parindent]
	\begin{equation}\begin{alignedat}{10}
			& \beta^{pw}_{mdkc}: \qquad 
				&& 	\sum_{dkc} \beta_{0dkc}^{pw} \Big( pw_{0dkc} - \gamma (pea_{dkc}) \Big) +
					\sum_{m=1dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
					\Big( pw_{mdkc} - \gamma 
					(\hat{pw}_{m-1dkc}) \Big) + \\
			& 
				&& \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
					\Big( pw_{mdkc} - \gamma 
					(\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big) + \\
			& 
				&& \sum_{dc} \beta_{Mdkc}^{pw} 
					\Big( pw_{Mdkc} - \gamma \sum_{M-1}^{M}
					(\hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] + E[pwt\_k_{k-1}] - E[pwt\_k_{k}]) \Big)
	\end{alignedat} \end{equation}
\end{fleqn}

@@

\begin{equation}\begin{alignedat}{10}
		&	v(S') = \Bigg( 
		&& 	\beta^0 + 
		\bigg( \sum_{p \in p\_co} \beta_{p}^{ul} (\hat{ul_{p}}) \bigg) +
			\bigg( \sum_{dc} \beta_{0dkc}^{pw} pea_{dkc} \bigg) +
			\bigg( \sum_{m=1,dkc}^{TL_{c}-1} \beta_{mdkc}^{pw} 
				(\hat{pw}_{m-1dkc} \bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{m=TL_{c}dkc}^{M-1} \beta_{mdkc}^{pw} 
		(	\hat{pw}_{m-1dkc} + E[pwt\_d_{m-1d-1c}] - E[pwt\_d_{d}] 
			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
		&	&&	\qquad \qquad \bigg( \sum_{dkc} \beta_{Mdkc}^{pw} 
		\sum_{M-1}^{M} ( \hat{pw}_{mdkc} + E[pwt\_d_{md-1c}] - E[pwt\_d_{d}] 
			+ E[pwt\_k_{k-1}] - E[pwt\_k_{k}])\bigg) + \\
		& 	&&	\bigg( \sum_{t=1m=1dkc}^{T-1, TL_{c}-1} \beta_{tmdkc}^{ps} 
				(\hat{ps}_{t+1m-1dkc}) \bigg) + \\
		&	&&	\qquad \bigg( \sum_{t=1m=TL_{c}dkc}^{T-1M-1} \beta_{tmdkc}^{ps} 
				(\hat{ps}_{t+1m-1dkc} + E[pst\_d_{t+1m-1d-1c}] - 
				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg)  + \\
		&	&&	\qquad \bigg( \sum_{t=1dkc}^{T-1} \beta_{tmdkc}^{ps} \sum_{M-1}^{M}
				(\hat{ps}_{t+1mdkc} + E[pst\_d_{t+1md-1c}] - 
				E[pst\_d_{d}] + E[pst\_k_{k-1}] - E[pst\_k_{k}]) \bigg) 
		\Bigg)
	\end{alignedat}
\end{equation}

### 2021-11-07 New-Manuscript/sections/mdp_model.tex
completed simulation

\subsection{State Space}
\subsubsection{Description}
State is defined by carried over resources, deviation from expected resources,, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1.
	\item $\vec{pw} = pw_{mdkc}$ - Patients of complexity $d$, priority $k$, surgery type $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
	\item $\vec{ps} = ps_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
\end{itemize}

\subsection{Action Sets}
\subsubsection{Description}
Decision consists of rescheduling currently scheduled patients, and scheduling patients on waitlist. There are also some goal and auxiliary variables
\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}, \text{auxiliary variables}) \] 
\begin{itemize}
	\item $\vec{sc} = sc_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, waiting for $m$ periods, to schedule in period $t$
	\item $\vec{rsc} = rsc_{tt'mdkc}$ -Patients of complexity $d$, priority $k$, surgery type $c$, waiting for $m$ periods, to reschedule from $t$ to $t'$
\end{itemize}

@@

\begin{equation}\begin{alignedat}{10}
		& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
		\overbrace{ \sum_{mdc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
			cost of waiting}  + 
		\overbrace{
			\sum_{tmdc} cs_{tk} (sc_{tmdkc})
		}^\text{Prefer earlier appointments} \\ 
		&	&&  +
		\overbrace{
			\sum_{
				\substack{tt`mdc \\ t' > t}} 
			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
		\overbrace{ 
			\sum_{
				\substack{tt`mdc \\ t' < t}}
			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
		M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

>>>>

\subsection{State Space}
\subsubsection{Description}
State is defined by carried over resources, deviation from expected resources, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1.
	\item $\vec{pw} = pw_{mdkc}$ - Patients of complexity $d$, priority $k$, surgery type $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
	\item $\vec{ps} = ps_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, scheduled to period $t$, waiting for $m$ periods
\end{itemize}

\subsection{Action Sets}
\subsubsection{Description}
Actions consist of rescheduling currently scheduled patients, and scheduling patients on wait list. There are also some goal and auxiliary variables
\[  \vec{A} = (\vec{sc}, \vec{rsc}, \text{auxiliary variables}) \] 
\begin{itemize}
	\item $\vec{sc} = sc_{tmdkc}$ - Patients of complexity $d$, priority $k$,  surgery type $c$, waiting for $m$, to schedule in period $t$
	\item $\vec{rsc} = rsc_{tt'mdkc}$ -Patients of complexity $d$, priority $k$, surgery type $c$, waiting for $m$, reschedule from $t$ to $t'$
\end{itemize}

@@

\begin{equation}\begin{alignedat}{10}
		& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
		\overbrace{ \sum_{mdkc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
			cost of waiting}  + 
		\overbrace{
			\sum_{tmdkc} cs_{tk} (sc_{tmdkc})
		}^\text{Prefer earlier appointments} \\ 
		&	&&  +
		\overbrace{
			\sum_{
				\substack{tt`mdkc \\ t' > t}} 
			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
		\overbrace{ 
			\sum_{
				\substack{tt`mdkc \\ t' < t}}
			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
		M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}
